State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-03 prism-backend/research/soa_review/ac.tex
Mention to Coconut.

@@

\begin{enumerate}
\item[\cite{cl01}:] Security in \cite{cl01} is proven in an ad-hoc way,
  using the ideal-world/real-world paradigm. The authors describe a
  simulator for the operations supported by the system (Setup, FormNym,
  GrantCred, VerifyCred and VerifyCredOnNym), and prove that the output of this
  simulator is indistinguishable from that of the real protocol, under the
  strong RSA and Diffie-Hellman assumptions.  
\item[\cite{cl02}:] No security model is given for the anonymous credential
  application of the signature scheme (reasonably, as it is not the main focus
  of the paper). The signature scheme is proven secure (no specific mention
  to a security model, although I suppose it would be quite straight forward)
  based on the Strong RSA and Diffie-Hellman assumptions.
\item[\cite{cl04}:] Same as in \cite{cl02} (no actual security model for the
  AC system). The custom proofs are based on the DDH and LRSW assumptions.
\item[\cite{cdhk15}:] The model (and associated proofs) presented in this paper
  is very comprehensive, and detailed. Specifically, for the main building block
  (Unlinkable Redactable Signatures), the authors give both game-based
  definitions as well as an ideal functionality. This ideal functionality models
  security in a single-issuer setting. However, as it is done in the UC
  framework, it can be composed with itself, so that a scenario with multiple
  issuers, in which users can combine credentials obtained by different users
  into a single showing process (``presentation'') is directly achievable by
  composing multiple instances of the ideal functionality (one per ``proof
  part'').
\end{enumerate}

@@

\begin{enumerate}
\item[\cite{cl01}:] Extensions provided to the main functionality are:
  \begin{itemize}
  \item PKI-based and all-or-nothing non-transferability: Both options
    involve sharing a verifiable encryption of the user secrets. In the
    case of PKI-based non-transferability, the CA receives a verifiable
    encryption, using as key the user's master secret, of some valuable
    piece of information belonging to the user (e.g., the user's secret
    key associated to his public key with that CA). In the all-or-nothing
    case, the user shares with each organization (with which it has a
    pseudonym), a verifiable encryption of his pseudonym secret data, encrypted
    with his master secret. In both cases, if the user shares his master
    secret with someone else, then he automatically gives access to
    other relevant pieces of information (as the verifiable encryptions are
    made public by the corresponding entity).    
  \item One-show credentials: The validating tags over pseudonyms are extended
    to include an extra value in their commitment. Then, users have to reveal
    that value (or, rather, a value deterministically derived from that) in the
    zero-knowledge proofs they create at show time. Since the value is always
    the same, verifiers can check whether they have seen it before, or not.
  \item Revocation: Both local (i.e., within an organization) and global (i.e.,
    referring to an identity of the user in an external CA) is possible by
    extending the pseudonyms of the user, and the credential showing protocols,
    with values that allow subsequent decryption by a trusted party of their
    pseudonym or external identity, given a transcript of the credential
    showing.    
  \item Attributes: The paper also succinctly describes how multiple attributes
    per credential could be included. This would be done by dividing the inverval
    within the exponent used to compute the pseudonym in sub-intervals, and then
    proving that the exponent lies within a sub-interval.
  \end{itemize}
\item[\cite{cdhk15}:] The same as in the previous works (\cite{cl01,cl02,cl04}).
\end{enumerate}

@@

@@

>>>>

\item[sms+19:] The Coconut system follows a similar approach than the previous
  works with respect to the representation and showing protocol for credentials.
  Namely, credentials are randomizable signatures issued blindly. In this case,
  the authors rely on Pointcheval Sanders signatures \cite{ps16} as main
  building block, to which they incorporate techniques from other schemes to
  support threshold issuance.

@@

\begin{enumerate}
\item[\cite{cl01}:] Security in \cite{cl01} is proven in an ad-hoc way,
  using the ideal-world/real-world paradigm. The authors describe a
  simulator for the operations supported by the system (Setup, FormNym,
  GrantCred, VerifyCred and VerifyCredOnNym), and prove that the output of this
  simulator is indistinguishable from that of the real protocol, under the
  strong RSA and Diffie-Hellman assumptions.  
\item[\cite{cl02}:] No security model is given for the anonymous credential
  application of the signature scheme (reasonably, as it is not the main focus
  of the paper). The signature scheme is proven secure (no specific mention
  to a security model, although I suppose it would be quite straight forward)
  based on the Strong RSA and Diffie-Hellman assumptions.
\item[\cite{cl04}:] Same as in \cite{cl02} (no actual security model for the
  AC system). The custom proofs are based on the DDH and LRSW assumptions.
\item[\cite{cdhk15}:] The model (and associated proofs) presented in this paper
  is very comprehensive, and detailed. Specifically, for the main building block
  (Unlinkable Redactable Signatures), the authors give both game-based
  definitions as well as an ideal functionality. This ideal functionality models
  security in a single-issuer setting. However, as it is done in the UC
  framework, it can be composed with itself, so that a scenario with multiple
  issuers, in which users can combine credentials obtained by different users
  into a single showing process (``presentation'') is directly achievable by
  composing multiple instances of the ideal functionality (one per ``proof
  part'').
\item[\cite{sms+19}:] No security model is given nor adopted.
\end{enumerate}

@@

\begin{enumerate}
\item[\cite{cl01}:] Extensions provided to the main functionality are:
  \begin{itemize}
  \item PKI-based and all-or-nothing non-transferability: Both options
    involve sharing a verifiable encryption of the user secrets. In the
    case of PKI-based non-transferability, the CA receives a verifiable
    encryption, using as key the user's master secret, of some valuable
    piece of information belonging to the user (e.g., the user's secret
    key associated to his public key with that CA). In the all-or-nothing
    case, the user shares with each organization (with which it has a
    pseudonym), a verifiable encryption of his pseudonym secret data, encrypted
    with his master secret. In both cases, if the user shares his master
    secret with someone else, then he automatically gives access to
    other relevant pieces of information (as the verifiable encryptions are
    made public by the corresponding entity).    
  \item One-show credentials: The validating tags over pseudonyms are extended
    to include an extra value in their commitment. Then, users have to reveal
    that value (or, rather, a value deterministically derived from that) in the
    zero-knowledge proofs they create at show time. Since the value is always
    the same, verifiers can check whether they have seen it before, or not.
  \item Revocation: Both local (i.e., within an organization) and global (i.e.,
    referring to an identity of the user in an external CA) is possible by
    extending the pseudonyms of the user, and the credential showing protocols,
    with values that allow subsequent decryption by a trusted party of their
    pseudonym or external identity, given a transcript of the credential
    showing.    
  \item Attributes: The paper also succinctly describes how multiple attributes
    per credential could be included. This would be done by dividing the inverval
    within the exponent used to compute the pseudonym in sub-intervals, and then
    proving that the exponent lies within a sub-interval.
  \end{itemize}
\item[\cite{cdhk15}:] The same as in the previous works (\cite{cl01,cl02,cl04}).
\item[\cite{sms+19}:] It is essentially the same as previous works, although it
  supports threshold issuance. Interestingly, \cite{sms+19} does not make use
  of pseudonyms. I.e., credentials are just signed (blocks of) attributes. This
  probably lets them achieve better efficiency. \doubt{This makes the scheme
    to be practically like a group signature scheme (without revocation...)}
\end{enumerate}

@@

\cite{sms+19} seems to be the most efficient one (note: relies on the
Fiat-Shamir heuristic). Credentials are only composed by two G1 elements,
independently on the number of attributes.

@@

Most schemes \cite{cl01,cl02,cl04,cdhk15,sms+19} are based on randomizable
signatures, with the possibility of signing committed values, that also support
efficient proofs of knowledge.

The most recurrent signature schemes are Camenisch-Lysyanskaya \cite{cl02,cl04},
BBS/BBS+ \cite{asm06,cdl16b}, and Pointcheval Sanders \cite{ps16}, with the
exception of \cite{cdhk15} that leverages their own signature scheme, called
Unlinkable Randomizable Signatures.
